Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-05-30 raspi_journal.tex
Wrote about TSNC

%=================================================================
\documentclass[electronics,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}

@@

To indicate which packets were used to generate a coded packet, one
form is to append its coding coefficients. In this case, the overhead
included for $C_i,\ \forall i \in [1,g]$ by the coding coefficients
is given by:
%
\begin{align} \label{eq:coded_packet}
|v_i| &= \sum_{j=1}^{g} |v_{i,j}| = g \times \lceil \log_{2} (q)
\rceil ~ [\mathrm{bits}]
\end{align}

@@

In \ac{SRLNC}, instead of considering all the packets to create a coded
packet like \ac{RLNC} does, here the encoder sets some coding coefficients to
zero when creating a new coded packet. This permits to reduce the complexity
of both the encoding and decoding operations since the encoder (or decoder)
requires less operations to process the data. Therefore, a new code parameter
to control the sparsity, the code density $d$, is included to vary the
number of non-zero packet that are combined. Here are various approaches to
set the density.

A first method is to specify the number of zeros in a given
generation size and later generate coded packets with this amount. For example:
16 zeros in a coding vector of 64 packets where the position of zeros are
modified at random for every coded packet generated. Another method is to
define an average number of zeros in the coding vector. Therefore, more or
less zeros are exactly generated for each coded packet in the process.
However, if not carefully made, using a sparse coding scheme might increase
the probability of generating \ac{l.d.} packets which incurs both overhead
from redundant information and processing delay.

@@

>>>>

%=================================================================
\documentclass[electronics,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
\synctex=1
\usepackage{fixme}

\newcommand\floor[1]{\lfloor#1\rfloor}

@@

To indicate which packets were used to generate a coded packet, one
form is to append its coding coefficients. In this case, the overhead
included for $C_i,\ \forall i \in [1,g]$ by the coding coefficients
is given by:
%
\begin{align} \label{eq:coded_packet_coef}
|v_i| &= \sum_{j=1}^{g} |v_{i,j}| = g \times \lceil \log_{2} (q)
\rceil ~ [\mathrm{bits}]
\end{align}

@@

In \ac{SRLNC}, instead of considering all the packets to create a coded
packet like \ac{RLNC} does, here the encoder sets more coding coefficients to
zero when creating a new coded packet.
In practice this can be implemented in
a couple of ways.
%One way to accomplish this is to add a Bernoulli random
%variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:
The simplest way to accomplish this is to add a Bernoulli random
variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:

\begin{align} \label{eq:sparse_coded_packet}
    C_i  &= \bigoplus_{j=1}^{g} \text{B}(d)_{j} \, v_{i,j} \otimes P_j ,\ \forall i \in [1,g] ,\
    v_{i,j} > 0,\
    d \in
    \begin{cases}
        {]0,0.5]} & \text{for } q=2 \\
        {]0,1]} & \text{for } q>2
    \end{cases}
\end{align}

We call $d$ the coding density.
Reducing $d$ enables the encoder to decrease the average number of packets that
are mixed into each coded packet. Thereby reducing the complexity of the
encoder that needs to mix less packets, but also on the decoder that in
contrast needs to eliminate less nonzero coding coefficients. The catch of this
approach is that coded packets produced by the encoder becomes more \ac{l.d.}
on each other as the coding complexity is reduced. This incurs in additional
channel overhead.

Generating a coded packet does not imply that it contains any data at all. I.e.
$ \left[ B(d)_{1}, \ldots, B(d)_{g} \right] = \mathbf{0}$.
In that case, one would have to trash the coded packet and generate a new one.

Most coded packets that are produced by the encoder are typically very sparse.
We will therefore rely on a slightly different implementation in KODO
\ref{eq:sparse_coded_packet2} that proved faster for low densities. It is best
expressed as:

\begin{align} \label{eq:sparse_coded_packet2}
    C_i  &= \bigoplus_{j=1}^{\floor{\text{Binom}(g,d)}} v_{i,m} \otimes P_{m} ,\
    %L \subseteq \{1,\dots,g\}: |L|=k ,\
    \forall i \in [1,g] ,\
    v_{i,j} > 0
\end{align}
where
$m = \text{choice}(\{1,\dots,g\}, \text{size}=k, \text{replace}=\text{False})$.
\fxnote{Can this be represented smarter?}

%To solve this, one could trash the coded packet and generate a new coded
%packet. This is not the most efficient because KODO needs to count the
%the number of nonzero coding coefficients in each coded packets to eliminate
%all zero packets.
%
%This is the most correct approach, but the most efficient approach although it is mathematically .

It is often desired to express the coding density as $d=\frac{k}{g}$. We call
this notation $k-sparse$ where $k$ is the average number of packets combined to
produce a coded packet.

%For low coding density, the encoder might generate a coded packet that consists
%of no coded packets. I.e. the packet consists of all zeroes

%In \ac{SRLNC}, instead of considering all the packets to create a coded
%packet like \ac{RLNC} does, here the encoder sets some coding coefficients to
%zero when creating a new coded packet. This permits to reduce the complexity
%of both the encoding and decoding operations since the encoder (or decoder)
%requires less operations to process the data. Therefore, a new code parameter
%to control the sparsity, the code density $d$, is included to vary the
%number of non-zero packet that are combined. Here are various approaches to
%set the density.
%
%A first method is to specify the number of zeros in a given
%generation size and later generate coded packets with this amount. For example:
%16 zeros in a coding vector of 64 packets where the position of zeros are
%modified at random for every coded packet generated. Another method is to
%define an average number of zeros in the coding vector. Therefore, more or
%less zeros are exactly generated for each coded packet in the process.
%However, if not carefully made, using a sparse coding scheme might increase
%the probability of generating \ac{l.d.} packets which incurs both overhead
%from redundant information and processing delay.

@@

\ac{TSNC} can be considered an extension to \ac{SRLNC}. The overall idea is
not only for the encoder to generate sparse coded packets, but also to
choose the sparsity of packets wiser. That is, as the decoder accomulates more
coded packets it becomes more and more likely that the next received
coded packet will be \ac{l.d.}.

The idea of \ac{TSNC} is therefore to gradually increase the coding density
as the decoderes \ac{DOF} increases. This enables TSNC to save a lot of
complexity particulary in the beginning of transmissions, but also to
tailor the coding delay. I.e. approximate the number of coded packets a
decoder needs to receive to decode a generation of $g$ packets. We call
this number the budget, $B$.

Provided a desired budget, $B \geq g$, and the decoders \ac{DOF} it can be
estimated how sparse the coded packets should be to finish a transmission in
time.

In our implementation, it is the encoders responsibility to estimate the coding
density. We use feedback to provide the encoder a better estimate of the
decoders \ac{DOF} at pre-defined points. Namely, when the decoder obtains the
following \ac{DOF}'s:

\begin{equation}\label{eq:feedback_dofs}
    s(k) = g\cdot \frac{2^k -1}{2^k},  \; \text{for } k=0,1,2,\dots,k_t 
\end{equation}
where $k$ is the $k$-th feedback packet that is transmitted during a generation.

The encoder considers the time between feedback packets as regions. It then
estimates a fixed coding density for each region when a feedback packet is
received.

Before the coding density can be estimated it is essential that the encoder
has a good estimate of the decoders \ac{DOF}, but also the remainder of the
total budget. The feedback scheme \ref{eq:feedback_dofs} roughly splits the
remaining \ac{DOF} in halves. This is also the case for the budget that is
split equally among the two new regions. The very last region will be asigned
the full remainder of the total budget.
